analysis

### 2020-01-01 03_Preliminary_analysis.Rmd
Remove old analyses

```{r rainLMadjrsquared}
ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_abline(intercept = 0, slope = 1, colour = "red")+
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu") 
```

@@

### Season range and first incidence

```{r first_incidence}
# Here I want to build a plot of horizontal lines indicating the season length and
# place a dot on the line to indicating the day of the year first sign was observed for that trial

season_dates <- PM_MB_means %>%
   group_by(trial_ref)%>%
   summarise(Planting_date = unique(planting_date),
             Harvest_date = unique(harvest_date),
             First_sign_PM = unique(first_sign_disease),
             season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
             )

@@

season_dates %>%
   ggplot()+
   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
   scale_y_continuous(
      limits = c(0, max(season_dates$Planting_day + 
                           season_dates$season_length, 
                        na.rm = TRUE)),
      labels = axis_labels_date,
      breaks = first_day_month
   )+
   geom_point(aes(x = trial_ref, y = Disease_day))+
   coord_flip()+
   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")

@@

#### Effect of Fungicide 
**on proportional yield gain with respect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r fungicide_proportion_yield}
PM_MB_means %>%
   group_by(fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

unique(PM_MB_means$fungicide)
# plot table as a box plot
PM_MB_means %>%
   filter(
      fungicide == c(
         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
         "200 g/L azoxystrobin + 80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole"
      )
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide)) +
   geom_boxplot() +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nFungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   coord_cartesian() +
   coord_flip()
#theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
#scale_x_continuous(limits = c(-0.3,0.6))

@@

Lets run this by a quick linear mixed effect model
```{r Fungicide_lmer}
levels(PM_MB_means$Fungicide)

PM_MB_means$Fungicide <-
   factor(
      PM_MB_means$Fungicide,
      levels = c(
         "control",
         "Propiconazole",
         "Tebeconazole",
         "Azoxystrobin",
         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
         "Carbendazim",
         "Benomyl",
         "Pyrazophos",
         "Acibenzolar-S-Methyl",
         "Sulphur",
         "Sulphur (SC)",
         "Sulphur (Ultra SC)",
         "Sulphur (WP)"
      )
   )

PM_MB_lmer.1 <-
   lmer(
      prop_YG ~ Fungicide * as.factor(total_Fungicide) + row_spacing + (1 |
                                                                           Trial_ref),
      data = subset(PM_MB_means, total_Fungicide == 1 |
                       total_Fungicide == 2)
   )

@@

How many trials contain all of the most studied fungicides
```{r Trials_with_top_three_Fungicides}
Tebe_trials <-
   unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole", ]$Trial_ref)
Propi_trials <-
   unique(PM_MB_means[PM_MB_means$Fungicide == "Propiconazole", ]$Trial_ref)
Azoxystrobin_trials <-
   unique(PM_MB_means[PM_MB_means$Fungicide == "Azoxystrobin", ]$Trial_ref)

intersect(intersect(Tebe_trials, Propi_trials)
          , Azoxystrobin_trials)

```{r Calculate_cuts, echo=FALSE}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   #   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(
      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")
   ))

days_from_fungicid <- function(FSD, F1, F2, F3) {
   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
   if (is.na(dF1)) {
      return(NA)
   } else{
      if (between(dF1, lower = -1, upper = 1000)) {
         return(dF1)
      } else{
         if (is.na(dF2)) {
            return(dF1)
         } else{
            if (between(dF2, lower = dF1, upper = -0.1)) {
               return(dF2)
            } else{
               return(dF3)
            }
         }
      }
   }
}
vec1 <- vector()
for (i in 1:dim(PM_MB_means1)[1]) {
   dF1 <-
      as.numeric(
         as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
      )
   dF2 <-
      as.numeric(
         as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
      )
   dF3 <-
      as.numeric(
         as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
      )
   if (is.na(dF1)) {
      vec1 <- c(vec1, dF1)
   } else{
      if (between(as.numeric(dF1), -1, 1000)) {
         vec1 <- c(vec1, dF1)
      } else{
         if (is.na(dF2)) {
            vec1 <- c(vec1, dF1)
         } else{
            if (between(as.numeric(dF2), as.numeric(dF1), -1.1)) {
               vec1 <- c(vec1, dF2)
            } else{
               if (is.na(dF3)) {
                  vec1 <- c(vec1, dF2)
               } else{
                  if (as.numeric(dF3) >= 0) {
                     vec1 <- c(vec1, dF2)
                  } else{
                     vec1 <- c(vec1, dF3)
                  }
               }
            }
         }
      }
   }
}
PM_MB_means1$spray_diff <-
   vec1 # gives the closest fungicide application date to the first sign of disease
#PM_MB_means1$days_from_1st

```{r Sulphur_efficacy, echo=FALSE}

# unique(
# PM_MB_means1 %>%
#    group_by(Fungicide) %>%
#    filter(n() >= 5) %>%
#    select(days_from_1st))
# 
# 
# PM_MB_means1 %>%
#    group_by(Fungicide) %>%
#    filter(n() >= 5) %>%
# ggplot(aes(prop_YG))+
#    geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
#    geom_vline(aes(xintercept = 0), size =0.5)+
#    facet_grid(rows = vars(cut(spray_diff, c(1,2,7,10,12,20))), cols = vars(Fungicide))+
#    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
#    labs(x = "Proportion of grain yeild saved",
#    title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
#    theme(panel.grid.major = element_line(colour = "grey80"),
#          panel.grid.minor = element_line(colour = "grey50"),
#          panel.background = element_rect(fill = NA))+
#    guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
#    scale_x_continuous(limits = c(-0.2,0.55))
# 
#

#__________________________________________________________________________________________________________
# levels(factor(PM_MB_means$Fungicide))

# combine Sulphur treatments
PM_MB_means2 <- PM_MB_means1 %>%
   filter(
      Fungicide == "Sulphur" |
         Fungicide == "Sulphur (SC)" |
         Fungicide == "Sulphur (Ultra SC)" |
         Fungicide == "Sulphur (WP)"
   )

unique(PM_MB_means2$spray_diff)

ggplot(PM_MB_means2, aes(prop_YG)) +
   geom_density(aes(fill = cut(
      PM_MB_means2$spray_diff, c(-30, -19, -15, -10, -1, 2, 7, 10, 12, 21)
   )), alpha = 0.5) +
   geom_vline(aes(xintercept = 0), size = 0.5) +
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30, -19, -15, -10, -1, 2, 7, 10, 12, 21)) ~
                 .) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(
      fill = guide_legend(title = "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")
   ) +
   scale_x_continuous(limits = c(-0.3, 0.6))

```
This plot shows that there is not a good probability that Sulphur will help save yield, even when it is sprayed at the ideal time.

```{r each_fungicide}
Chemical <-
   c("Azoxystrobin", "Carbendazim", "Tebeconazole", "Propiconazole")
levels(factor(PM_MB_means$Fungicide))

# Generates multiple plots for each type of fungicide tested
for (Chem in Chemical) {
   PM_MB_means2 <- PM_MB_means1 %>%
      filter(Fungicide == Chem)

   cat(Chem)

   # the following code 'spray_group' sets the spray_diff groupings that are used in the plots
   spray_group <- c(min(unique(PM_MB_means2$spray_diff)) - 1,
                    -5, 5,
                    max(unique(PM_MB_means2$spray_diff)) + 1)

   spray_group < -c(sort(unique(PM_MB_means2$spray_diff) - 1), max(unique(PM_MB_means2$spray_diff)))

   print(spray_group)

   p1 <- ggplot(PM_MB_means2, aes(prop_YG)) +
      geom_density(aes(fill = cut(PM_MB_means2$spray_diff, spray_group)), alpha = 0.5) +
      geom_vline(aes(xintercept = 0), size = 0.5) +
      facet_grid(cut(PM_MB_means2$spray_diff, spray_group) ~ .) +
      #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
      labs(x = "Proportion of grain yield saved",
           title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen") +
      theme(
         panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA)
      ) +
      guides(fill = guide_legend(
         title = paste(
            Chem,
            "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"
         )
      )) +
      scale_x_continuous(limits = c(-1, 1))

   print(p1)

}
```
It seems the calculation of spray diff does not elucidate any differences between application dates.

### Yield saved 
**Number of fungicide applications**
The following density plots show mean yield saved in relation to how many sprays were applied.

```{r PA_Yield, warning=FALSE, echo=FALSE}

# Making a table of showing the upper and lower percentiles (95%)
quant_PMy <- PM_MB_means %>%
   filter(fungicide != "control") %>%
   group_by(total_fungicide) %>%
   summarise(
      n = length(yield_gain),
      lower_2.5 = quantile(yield_gain, na.rm = T, c(0.025)),
      median = median(yield_gain, na.rm = T),
      mean = mean(yield_gain, na.rm = T),
      upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975))
   )

# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
ggplot(subset(PM_MB_means, fungicide != "control"), aes(yield_gain)) +
   geom_density(aes(
      group = factor(total_fungicide),
      fill = factor(total_fungicide)
   ), alpha = 0.6) +
   geom_vline(xintercept = 0, size = 1) +
   labs(x = "Grain yield saved (t/ha)",
        title = "Density plot of grain yield saved from differing numbers of fungicide applications") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   geom_vline(
      data = quant_PMy,
      aes(xintercept = lower_2.5,
          colour = factor(total_fungicide)),
      size = 0.9,
      linetype =  "dashed"
   ) +
   geom_vline(
      data = quant_PMy,
      aes(xintercept = upper_97.5,
          colour = factor(total_fungicide)),
      size = 0.9,
      linetype =  "dashed"
   ) +
   guides(
      colour = guide_legend(title = "Upper (97.5%) and \nLower (2.5%) percentiles"),
      fill = guide_legend(title = "Number of \nFungicide applications")
   ) +
   scale_x_continuous(limits = c(-0.3, 0.8))

kable(quant_PMy,
      caption = "Yield gain for each number of fungicide applications") %>%
   kable_styling(fixed_thead = T, full_width = T)

# Making a table of showing the upper and lower percentiles (95%)
quant_PM <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   group_by(total_Fungicide) %>%
   summarise(
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   )

# Density plot of proportion of yield saved
ggplot(subset(PM_MB_means, Fungicide != "control"), aes(prop_YG)) +
   geom_density(aes(
      group = factor(total_Fungicide),
      fill = factor(total_Fungicide)
   ), alpha = 0.6) +
   geom_vline(xintercept = 0, size = 1) +
   labs(x = "Proportion of grain yield saved",
        title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   geom_vline(
      data = quant_PM,
      aes(xintercept = lower_2.5,
          colour = factor(total_Fungicide)),
      size = 0.9,
      linetype =  "dashed"
   ) +
   geom_vline(
      data = quant_PM,
      aes(xintercept = upper_97.5,
          colour = factor(total_Fungicide)),
      size = 0.9,
      linetype =  "dashed"
   ) +
   guides(
      colour = guide_legend(title = "Upper (97.5%) and \nLower (2.5%) percentiles"),
      fill = guide_legend(title = "Number of \nFungicide applications")
   ) +
   scale_x_continuous(limits = c(-0.3, 0.55))

kable(quant_PM,
      caption = "Proportion of yield gain for each number of fungicide applications") %>%
   kable_styling(fixed_thead = T, full_width = T)
#knitr::kable(quant_PM,
#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
#caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season. Data from 2011-2017 mungbean experimental means. Data ignores factors such as fungicide, dose, season or location of experiment")
```

\n\n\n\n\n\n\n

#### Timing of Fungicide application
The following density plots show mean yield saved (t / Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.

```{r eval = FALSE, message = FALSE, warning = FALSE, include = FALSE}
PM_MB_means %>%
   filter(Fungicide != "control") %>%
   #   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(
      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")
   ))

```{r spray_timing&PropYield}
# What range of
unique(PM_MB_means1$days_from_1st)
PM_MB_means1 %>%
   group_by(cut(
      PM_MB_means1$days_from_1st,
      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
   )) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

ggplot(PM_MB_means1, aes(prop_YG)) +
   geom_density(aes(fill = cut(
      PM_MB_means1$days_from_1st,
      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
   )), alpha = 0.5) +
   geom_vline(aes(xintercept = 0), size = 0.5) +
   facet_grid(cut(
      PM_MB_means1$days_from_1st,
      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
   ) ~ .) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(
      fill = guide_legend(title = "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")
   ) +
   scale_x_continuous(limits = c(-0.2, 0.55))
```

>>>>

```{r rainLMadjrsquared}
ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu") 
```

@@

### Season range and first incidence
Mungbean is a summer crop and powdery mildew is requires cool conditions to establish. Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons. Can we visualise when PM is most likely to establish over the calender year.

I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.  
```{r first_incidence}
# Create the data frame for the plot
season_dates <- PM_MB_means %>%
   group_by(trial_ref)%>%
   summarise(Planting_date = unique(planting_date),
             Harvest_date = unique(harvest_date),
             First_sign_PM = unique(first_sign_disease),
             season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
             )

@@

# Plot
season_dates %>%
   ggplot()+
   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
   scale_y_continuous(
      limits = c(0, max(season_dates$Planting_day + 
                           season_dates$season_length, 
                        na.rm = TRUE)),
      labels = axis_labels_date,
      breaks = first_day_month
   )+
   geom_point(aes(x = trial_ref, y = Disease_day))+
   coord_flip()+
   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")

@@

In most years, regardless of the age of the crop, powdery mildew establishes in March.

#### Effect of Fungicide 
**Fungicide effect on proportional yield gain with respect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r fungicide_proportion_yield}
PM_MB_means %>%
   group_by(fungicide_ai) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

# plot table as a box plot
PM_MB_means %>%
   filter(
      fungicide_ai == c(
         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
         "200 g/L azoxystrobin + 80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "sulphur"
      )
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   geom_boxplot() +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nFungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   coord_flip()
#theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
#scale_x_continuous(limits = c(-0.3,0.6))

@@

Lets run this by a quick linear mixed effect model
```{r Fungicide_lmer}

PM_MB_means$fungicide_ai <-
   factor(
      PM_MB_means$fungicide_ai,
      levels = c(
         "control",
         "Propiconazole",
         "Tebeconazole",
         "Azoxystrobin",
         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
         "Carbendazim",
         "Benomyl",
         "Pyrazophos",
         "Acibenzolar-S-Methyl",
         "Sulphur"
      )
   )

class(PM_MB_means$trial_ref)

PM_MB_lmer.1 <-
   lmer(
      prop_YG ~ fungicide_ai * as.factor(n_treatment) + row_spacing + (1 |trial_ref),
      data = subset(PM_MB_means, 
                    n_treatment == 1 | n_treatment == 2)
   )

@@
